Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
removes meanwhile

\Cref{fig:moltres_radial_fluxes} compares the fast and thermal neutron fluxes at the
reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
moderator regions and visa versa in fuel regions are apparent. The flux
magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
calculations \cite[p. 92]{briggs_molten-salt_1964} as shown in
\cref{fig:msre_radial_fluxes}. The peak fast to thermal flux ratio is
approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
3 for the Moltres calculation. Meanwhile, control rod thimbles and
an extra volume of surrounding fuel not included in the Moltres calculations
cause the depression in the thermal flux in \cref{fig:msre_radial_fluxes}.

>>>>

\Cref{fig:moltres_radial_fluxes} compares the fast and thermal neutron fluxes at the
reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
moderator regions and visa versa in fuel regions are apparent. The flux
magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
calculations \cite[p. 92]{briggs_molten-salt_1964} as shown in
\cref{fig:msre_radial_fluxes}. The peak fast to thermal flux ratio is
approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
3 for the Moltres calculation. Control rod thimbles and
an extra volume of surrounding fuel not included in the Moltres calculations
cause the depression in the thermal flux in \cref{fig:msre_radial_fluxes}.
